### 2023-10-27 state/lstm.tex
Correctiion diogo state

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}
  \label{fig:lstmCell}
  \caption{\acs{LSTM} cell}
\end{figure}

@@

\begin{itemize}
  \item Removing the activation function from the Vanilla \ac{LSTM} for :
    \begin{itemize}
      \item the candidate cell and thus becomes $ \tilde{c}_t=(w_c\cdot[x_{t-1},h_{t-1}] + b_c) $, this is called the \ac{NIAF}
      \item the output of the previous cell state and thus becomes $ h_t=o_t\cdot c_t $, and is called \ac{NOAF}
    \end{itemize}
  \item Using units instead of the respective gates :
    \begin{itemize}
      \item \ac{NIG} : $i_t=1$
      \item \ac{NOG} : $o_t=1$
      \item \ac{NFG} : $f_t=1$
    \end{itemize}
\end{itemize}

>>>>

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}
  \label{fig:lstmCell}
  \caption{\acs{LSTM} cell, adapted from \cite{wikiLSTM}}
\end{figure}

@@

\begin{itemize}
  \item Removing the activation function from the Vanilla \ac{LSTM} for :
    \begin{itemize}
      \item the candidate cell and thus becomes $ \overrightarrow{\tilde{c}_t}=(w_c\cdot[\overrightarrow{x_{t-1}},\overrightarrow{h_{t-1}}] + \overrightarrow{b_c}) $, this is called the \ac{NIAF}
      \item the output of the previous cell state and thus becomes $ \overrightarrow{h_t}=\overrightarrow{o_t}\odot \overrightarrow{c_t} $, and is called \ac{NOAF}
    \end{itemize}
  \item Using units instead of the respective gates :
    \begin{itemize}
      \item \ac{NIG} : $\overrightarrow{i_t}=1$
      \item \ac{NOG} : $\overrightarrow{o_t}=1$
      \item \ac{NFG} : $\overrightarrow{f_t}=1$
    \end{itemize}
\end{itemize}

### 2023-10-27 state/main.tex
Forgot to rename the folders in the mains...
Corrected state of the art
Correctiion diogo state

This chapter will go over the several subject that need to be known in order to understand the thesis.

Math is the best way to universally describe all scientific models. For this reason, this chapter, and the thesis as whole, will contains equations.

It seems only logical to define all the tools that are going to be used in the thesis.

@@

\input{2.State/ai.tex}
\input{2.State/nn.tex}
\input{2.State/rnn.tex}
\input{2.State/lstm.tex}
\input{2.State/gru.tex}
\input{2.State/memristors.tex}
\input{2.State/crossbar.tex}
\input{2.State/model.tex}

>>>>

This chapter will go over the several subjects that need to be known in order to understand the thesis.

@@

\input{state/ai.tex}
\input{state/nn.tex}
\input{state/rnn.tex}
\input{state/lstm.tex}
\input{state/gru.tex}
\input{state/memristors.tex}
\input{state/crossbar.tex}
\input{state/model.tex}

### 2023-10-27 state/rnn.tex
Correctiion diogo state

\begin{equation}\label{eq:srnn}
  \overrightarrow{h_t}=tanh([\overrightarrow{x_t},\overrightarrow{h_{t-1}}]\cdot w + b)
\end{equation}

Where $t\in\mathbb{N}^*$ is the time index, $w$ the weight matrix, $b$ the bias matrix, $\overrightarrow{x_t}$ the input vector and $\overrightarrow{h_{t}}$ the hidden state of the \ac{RNN}.

>>>>

\begin{equation}\label{eq:srnn}
  \overrightarrow{h_t}=tanh([\overrightarrow{x_t},\overrightarrow{h_{t-1}}]\cdot w + \overrightarrow{b})
\end{equation}

Where $t\in\mathbb{N}^*$ is the time index, $w$ the weight matrix, $\overrightarrow{b}$ the bias vector, $\overrightarrow{x_t}$ the input vector and $\overrightarrow{h_{t}}$ the hidden state of the \ac{RNN}.
